---
title: "DSS"
output: html_document
---

```

## R Markdown

cause=unique(fire_cause)
```{r cause}
library(dplyr)
traindata<-data.frame(cause=data$STAT_CAUSE_DESCR,state=data$STATE,year=data$FIRE_YEAR)
res <- traindata %>% group_by(cause,state,year) %>% summarise(Freq=n())
#res1<-res[res$state=='CA',]
```

```{r cause}
library(ggplot2)
matrix1<-table(res$cause,res$year)
# The mtcars dataset:
matrix1<- as.matrix(matrix1)
# Default Heatmap
col<- colorRampPalette(c("red","tomato","salmon","tan1","yellow"))(256)
heatmap(matrix1, Colv = NA, Rowv = NA, col=col,scale="column",xlab = "years",main = "what causes the fire?")  
#col<- colorRampPalette(c("red", "white", "blue"))(256)
```

## Including Plots
```{R}
matrix2<-table(res$cause,res$state)
# The mtcars dataset:
matrix2<- as.matrix(matrix2)
# Default Heatmap
col<- colorRampPalette(c("mediumpurple1", "turquoise","cadetblue1" ,"yellow"))(256)

col<- colorRampPalette(c("red","tomato","salmon","tan1","yellow","khaki1"))(256)
heatmap(matrix2, Colv = NA, Rowv = NA, col=col,scale="column",xlab = "state",main = "what causes the fire for each state?")  
```

